---
title: "Movie Feature Analyis"
output: rmarkdown::github_document
---

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 120)
```


***This notebook mainly shows the relation between the target and the most critical features of a movie***

```{r message=FALSE}
require(MASS)
require(goftest)

load("../data/data_final/data_final.RData")
```


```{r}
plot(x = data_final$Kopien, y = data_final$Besucher_wochenende1_log,
     main = "Relation between number off copies and visistors on the first weekend", xlab = "#Copies", 
     ylab = "log(Visitors on the first weekend)")
```

The upper plot shows a clear relation between number of copies and the target feature. Obviously, this relation is not 
linear which should be taken into account if one includes this feature into her model.

```{r}
plot(x = data_final$Kinderfilm, y = data_final$Besucher_wochenende1_log,
     main = "Relation between the movie beeing a kids movie and visistors", 
     ylab = "log(Visitors on the first weekend)", xlab = "Kids Movie",  names = c("Yes", "No"))
```

Also there seems to be a relation between the movie beeing a Kids Movie or not. Whereby, Kids Movies usually attract 
less visitors that Non Kids Movies.

```{r}
par(mar = c(5, 10, 4, 2))
plot(x = data_final$Genre_Prognose, y = data_final$Besucher_wochenende1_log, horizontal=TRUE, las=2,
     main = "Relation between genre and visistors", xlab = "log(Visitors on the first weekend)", ylab = "")
```

If one takes a look at the relation between the visitors of a movie an its genre two points are highly remarkable: 
Thrillers and especially Drama and Arthouse movies seem to attract much less visitors than the other movie genres. On
the other hand Action/Adventure movies and CGI movies seem to attract much more than the average movie. The
remaining genres seem to attract an average number ob people with almost no outliers in the tranformed target.

The plot below shows the relation between the category of the stuio and the target feature. Unsurprisingly bigger
studios tent to release movies which attract a greater amount of visitors than the smaller independent studios.

```{r}
plot(x = data_final$Verleiherkategorie, y = data_final$Besucher_wochenende1_log,
     main = "Relation between studio category and visistors",
     ylab = "log(Visitors on the first weekend)", xlab = "Studio category")
```
