---
title: "Target Analyis"
output: rmarkdown::github_document
---

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 120)
```


***This notebook mainly shows the distribution of the target feature and tests for different distributions if the target
feature follows this distributions***

```{r message=FALSE}
require(MASS)
require(goftest)

load("../data/data_final/data_final.RData")
```
```{r}
truehist(data = data_final$Besucher_wochenende1, col = "grey", ylim = c(0, 0.00001), 
         xlab = "Visitors on the first weekend", ylab = "Density")
lines(x = density(data_final$Besucher_wochenende1), col = "black", lwd = 2)
grid = seq(from = 0, to = max(data_final$Besucher_wochenende1), by = 10)
lines(x = grid, y = dnorm(x = grid, mean = mean(data_final$Besucher_wochenende1), 
                          sd = sd(data_final$Besucher_wochenende1)), col = "red")
legend("topright", legend = c("KDE", "Normaldistribution"), col = (c("black", "red3")), lty = 1)
```

The target obviously isn't normal distributed.
Whereas, the logarithmic target seems to follow a normal distributionquite well.
```{r}
truehist(data = data_final$Besucher_wochenende1_log, col = "grey95", ylim = c(0.00, 0.25), ylab = "Density",
         xlab = "log(Visitors on the first weekend)")
lines(x = density(data_final$Besucher_wochenende1_log), col = "black", lwd = 2)
grid = seq(from = 0, to = max(data_final$Besucher_wochenende1_log) + 1, by = 0.1)
lines(x = grid, y = dnorm(x = grid, mean = mean(data_final$Besucher_wochenende1_log), 
                          sd = sd(data_final$Besucher_wochenende1_log)), col = "red3", lwd = 2)
legend("topright", legend = c("KDE", "Normaldistribution"), col = (c("black", "red3")), lty = 1)
```

The following tests check for normal distribution of the untransformed target:

```{r}
fit_normal = fitdistr(x = data_final$Besucher_wochenende1, densfun = "normal")
# Kolmogorov-Smirnov-Test:
ks.test(x = data_final$Besucher_wochenende1, y = "pnorm", mean = fit_normal$estimate[1], sd = fit_normal$estimate[2],
        exact = TRUE)
# Anderson-Darling-Test:
ad.test(x = data_final$Besucher_wochenende1, null = "pnorm", mean = fit_normal$estimate[1], sd = fit_normal$estimate[2])
# Cramer-von-Mises-Test:
cvm.test(x = data_final$Besucher_wochenende1, null = "pnorm", 
         mean = fit_normal$estimate[1], sd = fit_normal$estimate[2])
```

None of these test result in a p-value less than 0.05. Therefore, the Null hypothesis can be declined for all of these
tests and with it the assumption of the untransformed target feature following a normal distribution.

Let's have a look on the logarithmic target feature:
```{r}
fit_lognormal = fitdistr(x = data_final$Besucher_wochenende1, densfun = "lognormal")
# Kolmogorov-Smirnov-Test:
ks.test(x = data_final$Besucher_wochenende1_log, y = "pnorm", 
        mean = fit_lognormal$estimate[1], sd = fit_lognormal$estimate[2], exact = TRUE)
# Anderson-Darling-Test:
ad.test(x = data_final$Besucher_wochenende1_log, null = "pnorm", 
        mean = fit_lognormal$estimate[1], sd = fit_lognormal$estimate[2])
# Cramer-von-Mises-Test:
cvm.test(x = data_final$Besucher_wochenende1_log, null = "pnorm", 
         mean = fit_lognormal$estimate[1], sd = fit_lognormal$estimate[2])
```

In this case all of the tests have a p-value above 0.05, which leads to an acceptance of the Null hypothesis and 
confirms the impressions of the upper plots. The target feature seems to follow a log-normal distribution to a
statistically siginifcant degree.

A final test should also take the gamma distribution into consideration, which seems to fit the distribution of the 
target very well if one takes a look at the following plot:
```{r}
shape = mean(data_final$Besucher_wochenende1) ^ 2 / var(data_final$Besucher_wochenende1)
scale = var(data_final$Besucher_wochenende1) / mean(data_final$Besucher_wochenende1)
truehist(data = data_final$Besucher_wochenende1, col = "grey95", ylim = c(0.00, 0.00001), ylab = "Density",
         xlab = "log(Visitors on the first weekend)")
lines(x = density(data_final$Besucher_wochenende1), col = "black", lwd = 2)
grid = seq(from = 0, to = max(data_final$Besucher_wochenende1) + 1, by = 10)
lines(x = grid, y = dgamma(x = grid, shape = shape, scale = scale), col = "red3", lwd = 2)
legend("topright", legend = c("KDE", "Gamma Distribution"), col = (c("black", "red3")), lty = 1)
```

Applying the three tests results in the following ouputs:

```{r}
shape = mean(data_final$Besucher_wochenende1) ^ 2 / var(data_final$Besucher_wochenende1)
scale = var(data_final$Besucher_wochenende1) / mean(data_final$Besucher_wochenende1)
fit_gamma = fitdistr(x = data_final$Besucher_wochenende1, densfun = "gamma", start = list(shape = shape, scale = scale))
# Kolmogorov-Smirnov-Test:
ks.test(x = data_final$Besucher_wochenende1, y = "pgamma", shape = fit_gamma$estimate[1], scale = fit_gamma$estimate[2],
        exact = TRUE)
# Anderson-Darling-Test:
ad.test(x = data_final$Besucher_wochenende1, null = "pgamma", 
        shape = fit_gamma$estimate[1], scale = fit_gamma$estimate[2])
# Cramer-von Mises-Test:
cvm.test(x = data_final$Besucher_wochenende1, null = "pgamma", 
         scale = fit_gamma$estimate[1], shape = fit_gamma$estimate[2])
```

The Null hypothesis can be declined. Although, the p-values of all tests are above the p-values of the tests for 
normal distribution they are still far below a significant level of 0.05 which leads to the assumption that the target
features does not follow a gamma distribution.

Therefore, for all further descriptive analysis the logarithmic target feature will be used.

```{r}
# Boxpots
par(mfrow = c(1, 2))
boxplot(x = data_final$Besucher_wochenende1, ylab = "Visitors on the first weekend")
boxplot(x = data_final$Besucher_wochenende1_log, ylab = "log(Visitors on the first weekend)")
par(mfrow = c(1, 1))
```

```{r message=FALSE, include=FALSE, results='hide'}
par(mfrow = c(1, 1))
```

Also the boxplots of the untranformed and the logarithmic target varaible depict a much more balanced image of the 
logarithmic feature with much less outliers than the untransformed target.

```{r}
t_mon = as.POSIXlt(data_final$Kinostart)$mon + 1
t_y = as.POSIXlt(data_final$Kinostart)$year + 1900
t = as.Date(paste0(t_mon, "-", t_y, "01"), format = "%m-%Y%d")
tmp = aggregate(data_final$Besucher_wochenende1_log, by = list(t), mean)
colnames(tmp) = c("Date", "Visitors_log")
plot(tmp$Visitors_log ~ tmp$Date, type = "l", xaxt = "n", ylab =  "log(Visitors on the first weekend)", xlab = "Date")
axis.Date(side = 1, at = tmp$Date, format = "%m-%Y")
```

The developement of the target over time clearly shows a seasonal trend with peaks in winter and drops in spring and
summer. The final drop on summer of 2016 is due to the fact that the dataset does not contain as much movies for July
2016 as it does for the other months and therefore the monthly mean of July 2016 is more sensitive to outliers.